---
title: "Package Knapsack"
author: "Muhammad Faizan Khalid, Fahed Maqbool, Asad Enver"
date: "October 13, 2019"
output:
  html_document:
    toc: yes
    toc_depth: 2
  pdf_document:
    toc: yes
    toc_depth: '2'
  prettydoc::html_pretty:
    highlight: github
    theme: cayman
vignette: |
  %\VignetteIndexEntry{knapsackProblems} %\VignetteEncoding{UTF-8} %\VignetteEngine{knitr::rmarkdown}
---

A Package to solve knapsack problem using 3 different approaches.

## Kanpsack?
The knapsack is a discrete optimization problem where we have a sack that can filled with a limited **weight w** by adding **number of items i = 1, ..., n,** with a **weight wi** and a **value vi** to get the maximum value. This problem is `NP-hard, meaning that it is ”at least as hard as the hardest problem in NP”`
ref: ([via](https://en.wikipedia.org/wiki/NP-hardness))

## Three Different approaches to solve a knapsack problem
- brute force **brute force knapsack(x,w, parallel  = FALSE)**
- dynamic programming     **dynamic_program(x,w)**   
- greedy heuristic       **greedy_knapsack(x,w)**

##Parameters 

- **x** is a data frame which has two columns named **w** as weight column and **v** as value of each item.
- **w** is represent a scak capcaity to the sack can be filled.
- **parallel** which is only used in brute force search alogrithm if you want to run on mulitple core than set is as **TRUE**. The default value is set as **FALSE**

##generate a data

```{r}
devtools::load_all()
library("knapsackProblems")
set.seed(345) 
n <- 3000   
knapsack_objects <- data.frame( w=sample(1:4000, size = n, replace = TRUE),
                                v=runif(n = n, 0, 10000)
)

head(knapsack_objects) 
```


## brute_force_knapsack(x,w)


```{r, warning= FALSE, message= FALSE}
brute_force_knapsack(knapsack_objects[1:8,], w = 3500)
```

```{r, warning= FALSE, message= FALSE}
brute_force_knapsack(x = knapsack_objects[1:12,], w = 2000)
```

## How long does it takes to run the algorithm for n = 16 objects?

```{r}

set.seed(42) 
n <- 16  
knapsack_objects <- data.frame( w=sample(1:4000, size = n, replace = TRUE),
                                v=runif(n = n, 0, 10000))

system.time(result1 <- brute_force_knapsack(x = knapsack_objects[1:12,], w = 2000))
```


## dynamic_program(x, w)

```{r, warning= FALSE, message= FALSE}
dynamic_program(knapsack_objects[1:8,], w = 3500)
```

```{r, warning= FALSE, message= FALSE}
dynamic_program(x = knapsack_objects[1:12,], w = 2000)
```

## How long does it takes to run the algorithm for n = 500 objects?

```{r}

set.seed(42)
n <- 500
knapsack_objects <- data.frame( w=sample(1:4000, size = n, replace = TRUE),
                                v=runif(n = n, 0, 10000))
system.time(result2<- dynamic_program(x = knapsack_objects[1:12,], w = 2000))
```



## greedy_knapsack(x, w)

```{r, warning= FALSE, message= FALSE}
greedy_knapsack(knapsack_objects[1:800,], w = 3500)
```

```{r, warning= FALSE, message= FALSE}
greedy_knapsack(x = knapsack_objects[1:12,], w = 2000)
```

## How long does it takes to run the algorithm for n = 1000000 objects?

```{r}
set.seed(42) 
n <- 1000000  
knapsack_objects <- data.frame( w=sample(1:4000, size = n, replace = TRUE),
                                v=runif(n = n, 0, 10000))
system.time(result3 <- greedy_knapsack(x = knapsack_objects[1:12,], w = 2000))
```

## Paralellism brute force search
Paralellism is implemented in Brute Force algorithm to optimize performance of program. Usage of paralellism will be achieved by setting paralell parameter to TRUE in brute fore function.



## Microbenchmark package
Used for finding out the execution time of a function
```{r, echo=TRUE}
library(microbenchmark)

microbenchmark(
  "brute_force_knapsack"= result1, #n= 16
  "dynamic_program" = result2, #n= 500
  "greedy_knapsack" = result3 ,#n = 1000000
  times = 1,
  unit = "us"
)
```

